Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2016-10-11 code/rmarkdown/supporting_information.Rmd
+ article within page pnas limits

@@

@@

```{r, echo=FALSE}
write.table(loci_classification.DF, 'article/Table_S4.csv', sep=',', row.names=FALSE)
```

>>>>

# Figures

@@

# Tables

```{r, echo=FALSE}
write.table(loci_classification.DF, 'article/Table_S1.csv', sep=',', row.names=FALSE)
```

```{r, echo=FALSE, results='asis'}
curr.file <- tempfile(fileext='.tex')
x <- correlation.model.summary.DF %>%
	select(-contains('raw')) %>%
	mutate(
		Environmental.corr.P=pvalString(Environmental.corr.P),
		Geographic.corr.P=pvalString(Geographic.corr.P),
		Geographic.Marginal.R2=pvalString(Geographic.Marginal.R2),
		Geographic.Conditional.R2=pvalString(Geographic.Conditional.R2),
		Environmental.Marginal.R2=pvalString(Environmental.Marginal.R2),
		Environmental.Conditional.R2=pvalString(Environmental.Conditional.R2),
		blank=rep('', length(Species)),
		Species=paste0('\\textit{', gsub('\\ ', ' ', Species), '}')) %>%
	mutate(Environmental.Chisq=sapply(round(Environmental.Chisq,2), as.character)) %>%
	mutate(Geographic.Chisq=sapply(round(Geographic.Chisq,2), as.character)) %>%
	select(Species:Environmental.corr.P, Geographic.Marginal.R2:Geographic.corr.P) %>%
	latex(file=curr.file, 
		cgroup=c('', 'Environmental', 'Geographic'), n.cgroup=c(1, 4, 4), col.just=rep('c', 9),
		digits=2, rowname=NULL, first.hline.double=FALSE, booktabs=TRUE, here=TRUE,
		colheads=c('\\bfseries{Species}', '$MR^2$', '$CR^2$', '$\\chi^2$', '\\textit{P}', '$MR^2$', '$CR^2$', '$\\chi^2$', '\\textit{P}'),
		caption='Summary of maximum likelihood population-effects (MLPE) models. Briefly, for each species associated with potentially adaptive loci, a model was fit to correlate dissimilarities among planning units where the species in terms of the adaptive genetic characteristics of individuals in them with dissimilarities in terms of the environmental conditions inside the planning units (denoted in the environmental column group). Similarly, for each species, a model was fit to correlate dissimilarities among the planning units in terms of the neutral genetic characteristics of indiviudals in them with dissimilarities in terms of the geographic position of the planning units (denoted in the geographic column group). Data shows the results from comparing each model to its corresponding null model using $\\mathbf{\\chi^2}$ tests (1 degree of freedom), and the $\\mathbf{R^2}$ ($\\mathbf{MR^2}$) and conditional $\\mathbf{R^2}$ ($\\mathbf{CR^2}$) for each model.'
	)
readLines(curr.file)[-1] %>% paste0(collapse='\n') %>% 
	gsub(pattern='\\cline{1-', replacement='\\cline{2-6} \\cline{8-', fixed=TRUE) %>% 
	gsub(pattern='{c}{\\textit{P}}\\tabularnewline', replacement='{c}{\\textit{P}}\\T\\B\\tabularnewline', fixed=TRUE) %>% 
	gsub(pattern='\\toprule', replacement='', fixed=TRUE) %>%
	gsub(pattern='\\midrule', replacement='\\midrule', fixed=TRUE) %>%
	gsub(pattern='\\bottomrule', replacement='\\midrule', fixed=TRUE) %>%
	cat()
```

@@
